Transport map accelerated adaptive importance sampling, and application to inverse problems arising from multiscale stochastic reaction networks

### 2018-06-15 TPAIS_2018.tex
Added another section to discussion

\subsection{The Chicken and Egg Paradox}
Another issue with the use of transport maps of this ilk, is that in
order to construct such a map, we require a representative sample from
the posterior distribution. Since these methods are designed to sample
from distributions which are inherently difficult to sample from, be
it due to multimodality, as looked at in \cite{cotter2015parallel}, or
as in this paper, due to the density being highly concentrated close
to a curved manifold in parameter space, it could be argued that accessing this initial set of
samples remains a hard problem. This remains an open problem, which we
are aiming to address in future work.

>>>>

\subsection{Invertibility of the transport map}
In this paper, we have considered an approach very similar to that
deseminated in \cite{parno2014transport}, where we aim to find an
invertible map which approximates the true transport map between the
reference measure and the target measure, however this true map is
invariably itself not invertible. However, by considering embedding
the map in higher dimensions\cite{whitney_self-intersections_1994,nash1956imbedding,takens_detecting_1981}, these issues of non-invertibility may be
avoided, and higher quality maps may be found which better aid
exploration and sampling of the whole state space.

\subsection{The chicken and egg paradox}
Another issue with the use of transport maps of this ilk, is that in
order to construct such a map, we require a representative sample from
the posterior distribution. Since these methods are designed to sample
from distributions which are inherently difficult to sample from, be
it due to multimodality, as looked at in \cite{cotter2015parallel}, or
as in this paper, due to the density being highly concentrated close
to a curved manifold in parameter space, it could be argued that accessing this initial set of
samples remains a hard problem. This remains an open problem, which we
are aiming to address in future work.
